Accelerating Neural Network Training using Arbitrary Precision Approximating Matrix Multiplication Algorithms

### 2021-03-06 latex/MPP21/paper.tex
switching to new matmul perf data

In the performance results for 6 threads (\cref{fig:matmul_par_6}), we see that many of the algorithms start to outperform classical around dimension 2000, though some poor performance is observed for algorithms and particular matrix dimensions.
The fastest algorithms (e.g., $\dims{4,4,4}$ and $\dims{4,4,2}$) achieve a speedup of up to 23\% over \texttt{gemm} and exceed the machine peak for classical algorithms.
We note that the $\dims{4,4,2}$ algorithm has 24 subproblems, which is a multiple of 6, so there are no remainder subproblems that require all threads.

>>>>

In the performance results for 6 threads (\cref{fig:matmul_par_6}), we see that many of the algorithms start to outperform classical around dimension 2000, though some poor performance is observed for algorithms and particular matrix dimensions.
The fastest algorithms (e.g., $\dims{4,4,4}$ and $\dims{4,4,2}$) achieve a speedup of up to 25\% over \texttt{gemm} and exceed the machine peak for classical algorithms.
We note that the $\dims{4,4,2}$ algorithm has 24 subproblems, which is a multiple of 6, so there are no remainder subproblems that require all threads.
